Clustering in a hyperbolic model of complex networks.

### 2019-03-11 paper.tex
update to section 4
finished with section 9.2
pass over Sectoin 1-2.4 and fixed most references

\newcommand{\BallHyp}[1]{\Bcal\left(#1\right)}		%	The image of the hyperbolic ball around \Psi^{-1}(p)
\newcommand{\BallPo}[1]{\Bcal_{\infty}\left(#1\right)}		%	The neighborhood of a point p in the infinite limit model
\newcommand{\BallPon}[1]{\Bcal_{\text{box}}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
\newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\H,n}(#1)}		%
\newcommand{\BallSym}[1]{\Bcal_{\H \bigtriangleup \Pcal}\left(#1\right)}	%	Symmetric difference between balls in the 
																			%	hyperbolic and infinite limit model
\newcommand{\BallInter}[1]{\Bcal_{\H \cap \Pcal}\left(#1\right)}

@@

\newcommand{\hsym}[1]{h_{\H \bigtriangleup \Pcal}(#1)}
\newcommand{\EdgeDiff}{E_{\H \setminus \mathcal{P}}}
\newcommand{\expH}{\overline{n}_{\HP}(k_n)}
\newcommand{\expP}{\overline{n}_{\Pcal}(k_n)}
\newcommand{\Pop}[2]{\mathrm{Po} (#2;#1)}
\newcommand{\Nsymdiff}{N_{\H \bigtriangleup \Pcal}(k_n)}

@@

\newcommand{\Nbox}{\ensuremath{N_{\text{box}}}}
\newcommand{\Dbox}{\ensuremath{\text{deg}_{\text{box}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Don't mess with the tobimacros !!!!!							  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\eR}[0]{\ensuremath{{\mathbb R}}}
\newcommand{\eN}[0]{\ensuremath{{\mathbb N}}}
\newcommand{\Ee}[0]{\ensuremath{{\mathbb E}}}
\newcommand{\Haa}{\ensuremath{{\mathbb H}}}
\newcommand{\GPo}[0]{\ensuremath{G_{\text{Po}}}}
\newcommand{\Gbox}[0]{\ensuremath{G_{\text{box}}}}
\newcommand{\Ginf}[0]{\ensuremath{G_{\infty}}}
\newcommand{\isd}{\stackrel{\text{d}}{=}}
\newcommand{\Xcal}{\ensuremath{{\mathcal X}}}
\newcommand{\Ycal}{\ensuremath{{\mathcal Y}}}
\newcommand{\Qcal}{\ensuremath{{\mathcal Q}}}
\newenvironment{proofof}[1]{\vspace{1ex}\noindent{\bf Proof of #1:}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%								For leaving comments to each other:								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. Our results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should scale with $k^{-1}$ as we let $k$ grow. We find that this is true only when $\alpha > \frac34$, while $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\alpha < \frac34$ and $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac34$.
\end{abstract}

>>>>

\newcommand{\BallHyp}[1]{\Bcal\left(#1\right)}		%	The image of the hyperbolic ball around \Psi^{-1}(p)
\newcommand{\BallPo}[1]{\Bcal_{\infty}\left(#1\right)}		%	The neighborhood of a point p in the infinite limit model
\newcommand{\BallPon}[1]{\Bcal_{\text{box}}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
\newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\Po}(#1)}		%
\newcommand{\BallSym}[1]{\Bcal_{\Po \bigtriangleup \infty}\left(#1\right)}	%	Symmetric difference between balls in the 
																			%	hyperbolic and infinite limit model
\newcommand{\BallInter}[1]{\Bcal_{\Po \cap \text{box}}\left(#1\right)}

@@

\newcommand{\hsym}[1]{h_{\H \bigtriangleup \Pcal}(#1)}
\newcommand{\EdgeDiff}{E_{\H \setminus \mathcal{P}}}
\newcommand{\expH}{\overline{n}_{\Po}(k_n)}
\newcommand{\expP}{\overline{n}_{\infty}(k_n)}
\newcommand{\Pop}[2]{\mathrm{Po} (#2;#1)}
\newcommand{\Nsymdiff}{N_{\H \bigtriangleup \Pcal}(k_n)}

@@

\newcommand{\Nbox}{\ensuremath{N_{\text{box}}}}
\newcommand{\Dbox}{\ensuremath{\text{deg}_{\text{box}}}}
\newcommand{\Vbox}{\ensuremath{\mathcal{V}_{\text{box}}}}
\newcommand{\VPo}{\ensuremath{\mathcal{V}_{\Po}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Don't mess with the tobimacros !!!!!							  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\eR}[0]{\ensuremath{{\mathbb R}}}
\newcommand{\eN}[0]{\ensuremath{{\mathbb N}}}
\newcommand{\Ee}[0]{\ensuremath{{\mathbb E}}}
\newcommand{\Haa}{\ensuremath{{\mathbb H}}}
\newcommand{\GPo}[0]{\ensuremath{G_{\text{Po}}}}
\newcommand{\Gbox}[0]{\ensuremath{G_{\text{box}}}}
\newcommand{\GPoH}{\ensuremath{G_{Po,H}}}
\newcommand{\GboxH}{\ensuremath{G_{box,H}}}
\newcommand{\Ginf}[0]{\ensuremath{G_{\infty}}}
\newcommand{\isd}{\stackrel{\text{d}}{=}}
\newcommand{\Xcal}{\ensuremath{{\mathcal X}}}
\newcommand{\Ycal}{\ensuremath{{\mathcal Y}}}
\newcommand{\Qcal}{\ensuremath{{\mathcal Q}}}
\newenvironment{proofof}[1]{\vspace{1ex}\noindent{\bf Proof of #1:}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%								For leaving comments to each other:								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$. More precisely, $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac{3}{4}$ and $\gamma = \bigT{k^{-1}}$ when $\alpha > \frac{3}{4}$. These results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale with $k^{-1}$ as we let $k$ grow. 
\end{abstract}

### 2019-03-11 proof_overview_finite_k.tex
pass over Sectoin 1-2.4 and fixed most references

With this notation we then have that $\BallPo{p} \cap \Pcal$ denotes the set of neighbors of a vertex $p \in \Ginf$.
We will denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu = \mu_{\alpha, \nu}$, i.e. for every 
Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \, dx \, dy$

@@

For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P} \cap \Rcal$ and edge set such that
\[
	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
\]
where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$. 
Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting 
identified, which in particular 
%excludes boundary effects and 
makes the model invariant under horizontal shifts and reflections in vertical lines. 
The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some additional edges caused by 
the identification of the boundaries.

Similar to the infinite graph, for a point $p \in \Rcal$ we define the ball $\BallPon{p}$ as

\begin{equation}\label{eq:def_ball_P_n}
	\BallPon{p} = 
	\left\{p' \in \Rcal : |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}}\right\}.
\end{equation}

@@

Imagine that we have an infinite supply of i.i.d.~points $p_1, p_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution. In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $p_1,\dots, p_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$. In the {\em Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable 
with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $p_1,\dots, p_N$ and add edges 
according to the same rule as before. Equivalently, we could say that the vertex set consists of the points of a Poisson point process with intensity function $n g$, where $g$ denotes the probability density of the $(\alpha,R)$-quasi uniform distribution. That is,
\[
	g(r,\theta) = \frac{\alpha\sinh(\alpha r)}{2\pi(\cosh(\alpha R) - 1)} \cdot 1_{\{0\leq r\leq R, -\pi<\theta\leq \pi\}}.
\]

@@

\begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
Let $\mathcal{V}$ denote the vertex set of $\GPo(n;\alpha, \nu)$ and $\mathcal{W}$ the vertex set of $\Gbox(n;\alpha, \nu)$. 
Define the map $\Psi : [0,R] \times (-\pi, \pi] \to \Rcal$ by
\begin{equation}\label{eq:def_Psi}
	\Psi(r,\theta) = \left(\theta \frac{e^{R/2}}{2}, R - r\right).
\end{equation}
Then there exists a coupling such that, a.a.s., $\mathcal{W} = \Psi[\mathcal{V}]$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
%\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
%	\Prob{\Ccal_n^c} = \bigO{n^{-(2\alpha - 1)}}. 
%\end{equation}
\end{lemma}

@@

By the hyperbolic rule of cosines, for two points $p = (x,y) = \Psi( (r,\theta) ), p' = (x',y') = \Psi( (r',\theta') ) \in \Rcal$ we have that
$p' \in \BallHyp{p}$ iff.~either $r+r'\leq R$ or $r+r'>R$ and

$$
	\cosh r \cosh r' - \sinh r \sinh r'\cos\left( |\theta-\theta'|_{2\pi} \right) \le \cosh(R),
$$

\noindent
This can be rephrased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and

\begin{equation}\label{eq:def_Omega_hyperbolic}
	|x-x'|_{\pi e^{R/2}} \leq \Phi(r,r') := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh r \cosh r' - \cosh R}
	{\sinh r \sinh r'} \right).
\end{equation}

The following lemma provides useful bounds on the function $\Phi(r,r^\prime)$.

\begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R$ sufficiently large, the following holds.
For every $r,r^\prime \in [\varepsilon R,R]$ with $r + r^\prime > R$ we have that 
\begin{equation}\label{eq:asymp1}
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(r, r^\prime) 
	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R},
\end{equation}
where $y := R - r, y^\prime := R - r^\prime$. 
Moreover:
\begin{equation}\label{eq:asymp2} 
\Phi(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R - K$.} 
\end{equation}
\end{lemma}

@@

\begin{lemma}[{\cite[Lemma 30]{fountoulakis2018law}}]\label{lem:coupling_edges}
On the coupling space of Lemma~\ref{lem:coupling_hyperbolic_poisson} the following holds a.a.s.:
\begin{enumerate}
\item for any two points $p, p' \in \mathcal{W}$ with $y, y'\le R/2$, we have

$$pp' \in E(\Gbox) \Rightarrow \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo), $$

\item for any two points $p, p' \in \mathcal{W}$ with $y, y' \le R/4$, we have that

$$pp' \in E(\Gbox) \iff \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo).$$

>>>>

With this notation we then have that $\BallPo{p} \cap \Pcal$ denotes the set of neighbors of a vertex $p \in \Ginf$.
We will denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu = \mu_{\alpha, \nu}$, i.e. for every 
Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \dd x \dd y$

@@

For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\Vbox := \mathcal{P} \cap \Rcal$ and edge set such that
\[
	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
\]
where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$. Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting identified, which in particular makes the model invariant under horizontal shifts and reflections in vertical lines. The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\Vbox$, with some additional edges caused by the identification of the boundaries.

Similar to the infinite graph, for a point $p \in \Rcal$ we define the ball $\BallPon{p}$ as
\begin{equation}\label{eq:def_ball_P_n}
	\BallPon{p} = 
	\left\{p' \in \Rcal : |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}}\right\}.
\end{equation}

@@

Imagine that we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution. In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $u_1,\dots, u_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$. In the {\em Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable 
with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $u_1,\dots, u_N$ and add edges 
according to the same rule as before. Equivalently, we could say that the vertex set consists of the points of a Poisson point process with intensity function $n g$, where $g$ denotes the probability density of the $(\alpha,R)$-quasi uniform distribution. That is,
\[
	g(r,\theta) = \frac{\alpha\sinh(\alpha r)}{2\pi(\cosh(\alpha R) - 1)} \cdot 1_{\{0\leq r\leq R, -\pi<\theta\leq \pi\}}.
\]

@@

\begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
Let $\VPo$ denote the vertex set of $\GPo(n;\alpha, \nu)$ and $\Vbox$ the vertex set of $\Gbox(n;\alpha, \nu)$. 
Define the map $\Psi : [0,R] \times (-\pi, \pi] \to \Rcal$ by
\begin{equation}\label{eq:def_Psi}
	\Psi(r,\theta) = \left(\theta \frac{e^{R/2}}{2}, R - r\right).
\end{equation}
Then there exists a coupling such that, a.a.s., $\Vbox = \Psi[\VPo]$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
%\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
%	\Prob{\Ccal_n^c} = \bigO{n^{-(2\alpha - 1)}}. 
%\end{equation}
\end{lemma}

@@

By the hyperbolic rule of cosines, for two points $p = (x,y) = \Psi( (r,\theta) ), p' = (x',y') = \Psi( (r',\theta') ) \in \Rcal$ we have that $p' \in \BallHyp{p}$ iff.~either $r+r'\leq R$ or $r+r'>R$ and
\[
	\cosh r \cosh r' - \sinh r \sinh r'\cos\left( |\theta-\theta'|_{2\pi} \right) \le \cosh(R),
\]
This can be rephrased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and

\begin{equation}\label{eq:def_Omega_hyperbolic}
	|x-x'|_{\pi e^{R/2}} \leq \Phi(y,y^\prime) := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh(R-y) \cosh(R-y^\prime) - \cosh R}{\sinh(R-y) \sinh(R-y^\prime)} \right).
\end{equation}

The following lemma provides useful bounds on the function $\Phi(r,r^\prime)$. Note that in~\cite{fountoulakis2018law} the function $\Phi$ is written in terms of where $r := R - y, r^\prime := R - y^\prime$.

\begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R$ sufficiently large, the following holds.
For every $r,r^\prime \in [\varepsilon R,R]$ with $y + y^\prime < R$ we have that 
\begin{equation}\label{eq:asymp1}
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(y, y^\prime) 
	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R},
\end{equation}
Moreover:
\begin{equation}\label{eq:asymp2} 
\Phi(y,y^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $y, y^\prime > K$.} 
\end{equation}
\end{lemma}

@@

\begin{lemma}[{\cite[Lemma 30]{fountoulakis2018law}}]\label{lem:coupling_edges}
On the coupling space of Lemma~\ref{lem:coupling_hyperbolic_poisson} the following holds a.a.s.:
\begin{enumerate}
\item for any two points $p, p' \in \Vbox$ with $y, y'\le R/2$, we have 
\[
	pp' \in E(\Gbox) \Rightarrow \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo),
\]
\item for any two points $p, p' \in \Vbox$ with $y, y' \le R/4$, we have that 
\[
	pp' \in E(\Gbox) \iff \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo).
\]
